---
title: "project"
author: "Ramya and Lakshitha Parvataneni"
date: "04/04/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#libraries

```{r}
library("dplyr")
library("tidyr")
library("ggplot2")
library("caTools")
library("ROCR")
library("sqldf")
library("caret")
library("glmnet")
```


#Loading the data.
```{r}
imdb <- read.csv("imdb_database.csv",stringsAsFactors = FALSE)
head(imdb)
```

#Data Cleaning.

#Checking for null values in the columns and omitting them.
```{r}
colSums(is.na(imdb))

mvedata <- na.omit(imdb)

head(mvedata)

```
#Removing the columns which has all the null values.
```{r}
data1 <- select(mvedata,-c(Serie.Name,Serie.Date))
head(data1)
```
#Changing the Column Names.
```{r}
colnames(data1)<- c("movie_name","year","Genre","no_of_Votes","Revenue","Rating","Metascore","Duration","Director","Actors","Restriction","Description") 
head(data1)
```
#Removing the brackets & Punctuations from the column year.

```{r}

data1 <- mutate(data1,year = gsub("[\\(\\)]", " ",year))
head(data1)
data1 <- mutate(data1,year = gsub("–", "-", year))
head(data1)

```
#Converting the Revenue Column to numeric and substituting the null values with 0.
```{r}
l <- as.numeric(data1$Revenue)

data1 <- mutate(data1,Revenue = gsub("None", "0",Revenue))

View(data1)
```
#Exploratory Analysis.

#top 5 movies which has highest revenue.
```{r}
s<-top_n(data1, n=5, Revenue) %>%
          ggplot(aes(x=movie_name, y=Revenue,width = 0.5,fill = movie_name))+
geom_bar(stat='identity')+theme_minimal()+xlab("movie_name")+ylab("Revenue")

s
```

#Movie that has max number of votes.

```{r}

data2 <- data1 %>% 
select(movie_name,no_of_Votes) %>%
filter(no_of_Votes == max(no_of_Votes)) %>%
select(movie_name) 
data2




```


#Regression Analysis:

#We are predicting the Rating.

#Splitting of the dataset into train and test.
```{r}
splitdata <- sample.split(data1$Rating,SplitRatio = 0.05)
trainset <- subset(data1,splitdata==TRUE)
testset <- subset(data1,splitdata==FALSE)
View(trainset)
View(testset)

```

#Building the model.
```{r}
model <- lm(Rating ~ movie_name ,data = trainset)
summary(model)
```


```{r}
model2 <- lm(Rating ~ movie_name + year    ,data = trainset)
summary(model2)
```

```{r}
model3 <- lm(Rating ~ movie_name+year+Restriction+Duration , data = trainset)
summary(model3)
```
#passing the New data values to the model.

```{r}

new_data <- data.frame(wt=c("inception",2012,12,142))

new_data

```


#Predicted Data

```{r}
predict.model <- predict(model3,data = new_data)

View(predict.model)



```

```{r}
predict <- as.numeric(predict.model)
View(predict)

```

#Data frame for Actual and Predicted values

```{r}
options(stringsAsFactors = FALSE) 

pre_act <- data.frame(cbind(predict,actual = data1$Rating))
head(pre_act)
```

#plot  for predict and actual values.

```{r}
ggplot(pre_act,aes(x= predict,y= actual)) +
  geom_point()
```